---
title: "Kickin' Chikn"
output: 
  flexdashboard::flex_dashboard:
      theme: yeti
      storyboard: true
social: menu
source: embed
---
    
    ```{r setup, include=FALSE}
library(knitr)
library(flexdashboard)
library(RColorBrewer)
library(plotly)
require(rpivotTable)
require(openintro)
require(highcharter)
require(ggmap)
require(metricsgraphics)
require(readxl)
require(DT)
require(htmltools)
library(dygraphs)

ggmap::register_google(key = "AIzaSyCzk5YeyKH7zldNkLTr73C6ct6Ny6fUuys")


gdata <- read_xls("/Users/joehome/Desktop/AAMAIO/Data Visualization/us-zip-code-latitude-and-longitude.xls")


engdata <- read_xlsx("/Users/joehome/Desktop/AAMAIO/Data Visualization/Engagement and Revenue.xlsx")

data <- read.csv("/Users/joehome/Desktop/AAMAIO/Data Visualization/EmployeeData.csv", row.names = 1)


timedata <- read_xlsx("/Users/joehome/Desktop/AAMAIO/Data Visualization/Daily Engagement.xlsx")
```



### Regional Data 

```{r}
#make a map, create a subset
gdata <- subset(gdata, select = -c(Zip, City, State, 
                                 Timezone, geopoint))
#i want the US, maptype is google maps, with color
map1 <- ggmap(get_googlemap(location = 'united states',
                                maptype = "hybrid",
                            zoom = 4,
                            source = 'google',
                            color = "color"))


# add a layer, x is long, y is lad. colored by revenue.

#add a gradient for revenue

map1 + geom_point(aes(x = Longitude, y= Latitude,
                  color = Revenue),
              data = gdata, size = 0.5) +
                theme(legend.position = "right") +
                      scale_color_gradient(low = "red", high = "green")


```

***
Takeaways

- The Northeast and Southeast seem to drive revenue this year

- COVID has driven down a large portion of store profit


### Employee Data (Store #00929) 


```{r}

#create a matrix for plotly
data <- as.matrix(data)


#divide cell values by column mean
data1 <- apply(data, 2, function(x){x/mean(x)})

#z is data, make a heatmap and specify size parameters

plot_ly(x=colnames(data1),
        y=rownames(data1),
        z=data1,
        width = 700,
        height = 700,
        type = "heatmap",
        colors = "RdYlGn")

```

***
Takeaways

- There is not much variation in many of the categories

- Complaints and movement seem to be related for some employees

- There may be a couple of bad apples 

### Daily Engagement 

```{r}

#html widget dygraph, specify labels and sizing, add a range selector

d <- dygraph(timedata,
        main = "Engagement",
        ylab = "Day",
        width = 600,
        height = 270)
    dyRangeSelector(d)
```

***
Takeaways

- Engagement has dropped off substantially


### Top Employees

```{r}
datatable(data, options = list(pageLength = 10))
```



### Regional Performance

```{r}

#examine reported regional performance

x <- c('Northeast', 'Northwest', 'South', 'Midwest')
y <- c(90, 62, 85, 75)


#frame
regdata <- data.frame(x,y)

#ggplot, fill based on x variable

#geom bar for barplot

regchart <- ggplot(data = regdata, aes(x= x, y=y,
            fill=x)) +
            ggtitle("Regional Performance") +
            geom_bar(stat="identity") +
            xlab("Region") + ylab("Job Performance") + 
            theme(legend.position = 'none')

regchart
                


```


***
Takeaways

- The Northeast has the highest job performance, the Northwest seems to be lagging behind

### Regional Engagement

```{r}

#look at regional engagement


x2 <- c('Northeast', 'Northwest', 'South', 'Midwest')
y2 <- c(75, 21, 74, 70)

regeng <- data.frame(x2,y2)

#samesies

regengdat <- ggplot(data = regeng, aes(x= x2, y=y2,
            fill=x2)) +
            ggtitle("Regional Engagement") +
            geom_bar(stat="identity") +
            xlab("Region") + ylab("Engagement") +
            theme(legend.position = 'none')


regengdat
    
```


***
Takeaways

- Regional Engagement sees similar trends

- Engagement is very low in the Northwest


### Engagement and Revenue



```{r}


#interactive html widget

#height, color and size it based on revenue
mjs_plot(engdata, x=Engagement, y=Revenue, width = 600, height = 500) %>%
    mjs_point(color_accessor=Revenue, size_accessor=Revenue) %>%
    mjs_labs(x="Engagement", y="Daily Revenue")



```


***
Takeaways

- Based on a recent survey, engagement seems to be highly related to daily revenue



